Unitary evolution as a quasistatic process of infinitesimal collapses

### 2019-04-19 Articles/2019-ForQuantumOptics/MDPI_template/template.tex
Finalized version for submission

\documentclass[11pt]{article}

\usepackage[margin=1.25in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{dutchcal}
\usepackage{braket}
\usepackage{enumitem}

\usepackage{tikz}
\usepackage{forest}
\usetikzlibrary{trees}
\usetikzlibrary{calc}
\usepackage{calculator}
\usepackage{standalone}

\usepackage{braket}

\begin{document}

\title{Unitary evolution as a quasistatic process of infinitesimal collapses}

\maketitle

\begin{abstract}
Any state, to be properly defined, has to be an equilibrium of all processes happening at a faster timescale. As processes with equilibria are idempotent, they can be expressed as projections in a probability space. Assuming a quasistatic evolution, then, means the equilibria of the faster scale processes will evolve slowly, giving rise to continuous and unitary evolution. These ideas are sufficient to get the general form of the projection postulate and the time evolution of quantum mechanics. Violations of the Schroedinger equation, then, should be expected only for processes that cannot be considered quasistatic.
\end{abstract}

%\tableofcontents
%\newpage

\section{Introduction}

In an effort to better understand why the frameworks of classical and quantum mechanics are what they are, we have worked on identifying a minimal set of physical assumptions from which both can be derived.[cite] This gave us a new perspective that is somewhat unusual among people who work on fundamental questions in physics. The typical view is that the theories are so different that they require a radically different set of starting points, and that classical mechanics in particular should only be viewed as an approximation of quantum mechanics. In this view, the similarities between the theories stem from one being an approximation of the other.

@@

In this paper we outline the fundamental elements of a generic model for a physical system, their relationships and, in particular, how they work in the context of quantum mechanics. The general idea is that for a state to be experimentally prepared, manipulated and measured, it needs to be ``stable'' for what may be a very short but certainly finite amount of time. That is, it must be a, possibly metastable, equilibrium of faster scale processes. But a process for which all outputs are equilibria is idempotent (i.e. gives the same output no matter how many times it is applied) and is therefore mathematically modeled by a projection operation on the space of statistical distributions. We identify quantum projections as these processes. If we want a deterministic law, then, it must be a quasistatic evolution in terms of those faster scale processes. As the change must be small, this leads to continuous evolution over the state space and unitary evolution in the space of statistical distributions. We identify unitary evolution as this deterministic law.

@@

In quantum mechanics, not all statistical ensembles are distinguishable from each other. For example, in the spin $1/2$ case, the distribution $\mathcal{d}_1$ defined as $\mathcal{d}_1(z^+)=\mathcal{d}_1(z^-)=\frac{1}{2}$ is physically equivalent to $\mathcal{d}_2$ defined as $\mathcal{d}_2(x^+)=\mathcal{d}_2(x^-)=\frac{1}{2}$. Therefore we define the set of mixed states $\mathcal{M}$ as the set of statistical ensembles that are physically different, which is usually represented by a density matrix. Mathematically, we can also represent physical equivalence between statistical ensembles with the equivalence operator $\mathcal{d}_1 \equiv \mathcal{d}_2$ and the set of mixed states $\mathcal{M} = \mathcal{D}_{/_\equiv}$ will be the quotient space.

@@

We can briefly see why this approach makes intuitive sense. The closer two states are in the Hilbert space, the greater the chance that one will transition to the other during a projection. Continuous evolution, then, means small deterministic changes. Unitary evolution, in particular, conserves entropy, which is also the hallmark of deterministic and reversible evolution. On the other hand, a projection can increase entropy, which is the hallmark of a transition that went out of equilibrium and is not reversible. Since any two unitary vectors can be connected by a unitary operation (i.e.~a rotation), it makes sense that all states are equilibria since they can all be connected by a deterministic and reversible process and that they all carry the same entropy. We also note that in quantum field theory, to calculate cross-sections and particle decays, one puts the initial states at minus infinity and the final states at plus infinity for processes that, in reality, take a tiny fraction of a second. This is reminiscent of a quasistatic approximation. Finally, while the approach presented here does not solve the so called ``measurement problem'', it does however give us an understanding of why we have the problem to begin with: our states are really just the equilibrium states of faster scale processes and those cannot, in general, be described by quasistatic ones.

@@

With this is mind, let us explore the following question: could we, in principle, extend the state to exhaust the description of the system? As we saw, that would mean finding a set of circumstances in which the evolution of the entirety of the system is fully determined by the system itself. That is, no part of the system is influenced by the environment in any way. Under those conditions, no interactions with the system are possible. Photons cannot scatter off of it, nor gravitational waves; no way to synchronize clocks between the system and the environment, no way to tell where the system is with respect to the environment. To us in the environment, within those circumstances, the system has vanished. How, then, are we supposed to study it? How are we supposed to experimentally define the properties in those conditions? How are we supposed to validate the law of evolution?

This tells us that there is a tension. On one side we can only say that something is a property of the system if it is defined independently of the environment. On the other side, we cannot completely turn off system-environment interaction or there would be no way to operationally define the property. This means that we can never have a complete independent description of the system.\footnote{Ultimately, this is why classical mechanics conceptually fails. See XXX for more discussion.} We need to leave out some ``unstated part'' whose future will depend on the environment. In other words, \textbf{the system always has a boundary with the environment and, through it, is in constant interaction}.

This unavoidable interaction with the environment also comes into play in the definition of a system and its state. For example, we can talk about the position of a ball because we sit on the surface of the earth at around 273 K. If we were on the surface of the sun at around 5778 K, after a short time, we would not be able to talk about a ball. A state and its properties only exist because the system is in some kind of equilibrium with the environment. Therefore even if the unstated part is not part of the state, its interaction with the environment has to be ``suitable'' for the state to be defined in the first place. In other words, \textbf{a physical property of a system is well defined and measurable if and only if the constant interaction with the environment keeps it that way.}\footnote{A possible misconception here is thinking of a process that does not change anything as ``doing nothing''.}

@@

Every process that has equilibria is characterized by a time scale needed to reach equilibrium. That time will set the maximum time resolution we can use with that choice of states and processes. To go to faster time scales we inevitably need to change both states and processes. For example, as we change the volume of a gas, the region against the moving wall will be compressed sooner than the opposite region, but if we wait a short while we will again obtain a uniform pressure. If we want to study that transition, we may conceptually divide the system into small volumes and the pressure is replaced by a pressure field. Still, we need to assume each small volume to have enough molecules to be in equilibrium. We can go into more detail, and describe the distribution of position and velocities of the molecules. Yet, we need to assume that the molecules themselves are not undergoing chemical changes. We could study the atoms of the molecules, yet we would have to assume that the atoms are stable under nuclear fission. We could study the electrons and nucleons of the atoms, yet we would have to assume they are stable under weak nuclear forces. As we move to a finer and finer description, we have faster and faster scale processes that we assume do not change the basic constituents. At each level of the description what is assumed to be in equilibrium changes and what the laws describe changes as well. Yet, the overall structure remains the same: we have a timescale $dt$ such that within each interval $[t-dt, t]$ there is a process $\mathcal{p}_t$ such that the state $\mathcal{s}_t$ is an equilibrium of $\mathcal{p}_t$. The evolution $\mathcal{E}$, then, is quasistatic in terms of the processes in $\mathcal{P}$. That is, \textbf{all deterministic laws are quasistatic evolutions in terms of system-environment interaction processes}.

We have reached, then, the second major point of this article: \textbf{the mathematical structure we used to rearrange quantum mechanics is a general structure that applies to all systems} and as such we call it the \emph{fundamental model of physics}. It is fundamental because it always applies and what changes case by case are the specifics. If we study a ball using classical particle mechanics, for example, the position and momentum of the center of mass will be defined in a short time scale integrating the jiggling created by the random collisions of air particles. That averaging process will be the same regardless of the values of position and momentum; all states are equilibria of the same process and therefore $\mathcal{P}$ contains only one element: the identity map. Therefore, while the overall structure still exists, it is mathematically trivial and can be effectively disregarded as we concentrate on the law of evolution exclusively.

@@

In this framework all processes in $\mathcal{P}$ always represent abrupt transitions to a new equilibrium. In thermodynamics they could represent the crystallization of a supersaturated solution or the ignition of a mixture of oxygen and hydrogen to form water. In quantum mechanics they represent the absorption of an incoming photon by a hydrogen atom or the decay of a muon into an electron and two neutrinos. In all these cases we start from a state of (possibly metastable) equilibrium and we end with a new equilibrium which is not, in general, described in terms of the initial state space. For example, water vapor is not a mixture of hydrogen and oxygen gases and a muon is not a collection of three particles. That is, in general the system passes through configurations that are not suitably described by the initial or final state space. We do not believe the similar conceptual structure to be simply a formal analogy but to represent analogue physical mechanisms. Quantum projections happen for the same reasons supersaturated solutions crystallize: an abrupt change in external or internal physical conditions.

Why, then, are measurements in quantum mechanics typically associated with projections? Let us think of what a particle detector has to do: it has to take the very small signal of a particle coming through and amplify it to a macroscopic level. In the case the particle itself is absorbed, or destroyed in any way, then we are already in the realm of fast processes. In the other cases, the particle has to initiate a chain reaction that has to transfers energy stored in the detector system to the readout. The detector, then, has to be prepared in a state sufficiently stable to not change if no particle interacts with it but unstable enough that a small perturbation makes it transition to a lower energy. That is, the detector has to be prepared in a metastable state and the particle interaction has to make it transition to a more stable state. But a transition from a metastable state to a more stable state is exactly what our projections are supposed to represent. %https://www.researchgate.net/publication/280330121_A_Heuristic_Approach_to_the_Quantum_Measurement_Problem_How_to_Distinguish_Particle_Detectors_from_Ordinary_Objects

@@

Violations of the Schroedinger equation, then, should be expected only for processes that cannot be considered quasistatic. If we were to implement a measurement process, then, in a way that the transfer of information between the system and the probe happens in a slow and controlled fashion, this could not provide a violation of the Schroedinger equation, nor would it tell us that all projections are quasistatic processes. A better description of the faster scale processes given by the projections, then, will inevitably need a new state space as the standard quantum states only describe equilibria, and we should expect the faster scale processes to go out of equilibrium. Consequently, a description at Planck time scale will ultimately fail to be continuous and quasistatic since a finite change in a finite time will not be divided into infinitesimal adiabatic changes over infinitely many time steps.

To understand the suitable mathematical framework for those regimes where unitary evolution may not hold, we are proceeding by first identifying the physical requirements for all mathematical structures already used in physics, starting from the most basic ones like topological spaces (upon which is based all of differential geometry) and $\sigma$-algebras (upon which is based all of measure theory and probability theory). This long term effort is centered mainly around the development of an open access book in which these issues can be explored in full detail and with a rigor more typical of mathematical disciplines. This rigor forces us to spell out the often hidden assumptions we have while constructing physical theories. By making explicit, for example, under which physically motivated circumstances time can be modeled by real numbers, or when states can be represented within Hilbert spaces, we believe we will be in a better position to understand what happens when those assumptions fail.

%\section{???}

%If we accept the line of thinking present in the previous two sections, we can try and draw some conclusions. These will be necessary qualitative as much further work would be needed to make any quantitative prediction.

%The first main conclusion is that we should be able to find processes that are neither described by unitary evolution nor by the projection. These would correspond to processes for which the out-of-equilibrium dynamics becomes relevant so the quasistatic evolution is not a good approximation and neither is the instantaneous transition. Even if we do not have a theory for those regimes, we can, at least conceptually, discuss a couple of general strategies.

%For example, we can note that slow changing conditions are unlikely to reveal new dynamics. As long as the system evolves continuously, the quasistatic approximation will hold. It is also conceivable that, in some conditions, a process that may look like a projection end-to-end is actually well described by a slow transition. In those cases the quasistatic approximation evidently holds and no new phenomena would be observed. What is the right time scale, though, is not clear to us since ``slow'' in this setting is still ``very fast''.

%The main issue is that we have to catch the system out of equilibrium. In principle, we can imagine preparing a state $\mathcal{s}_0$, starting a process $\mathcal{p}_1$ and, while in transition, switch to process $\mathcal{p}_2$. At that point, the final state may have characteristics that are different from having run the two process sequentially and that would be evidence of new physics. Hypothetically, this may correspond to having an atom absorb a photon while it was already in the process of emitting one. Or it may correspond to polarizing a particle horizontally while it was in the process of polarizing vertically. Whether anything along these lines is actually practicable is unclear, but it's one general strategy.

%Another one would be to find a process that under some conditions is well described by unitary evolution while in others by a projection. We may find that at the boundary of the transition the process will be described by neither. This may correspond, for example, to those cases where an energy threshold has to be passed to see particle productions or particle absorption. It is not clear what kind of precision would be required to elicit a different response, but it's general strategy.

%The second main conclusion is that to get a more fundamental theory we have to change the state space. As quantum states only characterize the equilibria for the projections, we need a different state space for the out-of-equilibrium states. This suggests that developing the right physical model for what happens during a projection is not a simple matter of finding a suitable Hamiltonian or a non-linear law of evolution. We may have to substitute complex Hilbert spaces with something else. Given that we don't even have consensus on why those spaces are needed in the first place, and on whether all the objects in those spaces are actually physical, it is unclear what we would substitute them with.

>>>>

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[applsci,article,submit,moreauthors,pdftex]{Definitions/mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

\usepackage{braket}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{dutchcal}

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Unitary evolution as a quasistatic process of infinitesimal collapses}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-1071-6251} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-9540-4988} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Gabriele Carcassi $^{1}$\orcidA{}* and Christine A. Aidala $^{1}$\orcidB{}}

% Authors, for metadata in PDF
\AuthorNames{Gabriele Carcassi and Christine Aidala}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA}

% Contact information of the corresponding author
\corres{Correspondence: carcassi@umich.edu}

% Current address and/or shared authorship
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Any state, to be properly defined, has to be an equilibrium of all processes happening at a faster timescale. As processes with equilibria are idempotent, they can be expressed as projections in a probability space. Assuming a quasistatic evolution, then, means the equilibria of the faster scale processes will evolve slowly, giving rise to continuous and unitary evolution. In this paper we show that these ideas are sufficient to get the general form of the projection postulate and the time evolution of quantum mechanics, while also creating a model that applies to other physical theories, such as classical mechanics and thermodynamics. In this light, the different theories are specializations of a broader model. As unitary evolution corresponds to quasistatic evolution, violations of the Schroedinger equation, then, should be expected only for processes that cannot be considered quasistatic. }

% Keywords
\keyword{foundations of quantum mechanics; quasistatic evolution; processes and equilibria}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

In an effort to better understand why the frameworks of classical and quantum mechanics are what they are, we have worked on identifying a minimal set of physical assumptions from which both can be derived.\cite{Carc1} This gave us a new perspective that is somewhat unusual among people who work on fundamental questions in physics. The typical view is that the theories are so different that they require a radically different set of starting points, and that classical mechanics in particular should only be viewed as an approximation of quantum mechanics. In this view, the similarities between the theories stem from one being an approximation of the other.

@@

In this paper we outline the fundamental elements of a general model for a physical system, their relationships and, in particular, how they work in the context of quantum mechanics. The basic idea is that for a state to be experimentally prepared, manipulated and measured, it needs to be ``stable'' for what may be a very short but certainly finite amount of time. That is, it must be a, possibly metastable, equilibrium of faster scale processes. But a process for which all outputs are equilibria is idempotent (i.e. gives the same output no matter how many times it is applied) and is therefore mathematically modeled by a projection operation on the space of statistical distributions. We identify quantum projections as these processes. If we want a deterministic law, then, it must be a quasistatic evolution in terms of those faster scale processes. As the change must be small, this leads to continuous evolution over the state space and unitary evolution in the space of statistical distributions. We identify unitary evolution as this deterministic law.

@@

In quantum mechanics, not all statistical ensembles are distinguishable from each other. For example, in the spin $1/2$ case, the distribution $\mathcal{d}_1$ defined as $\mathcal{d}_1(z^+)=\mathcal{d}_1(z^-)=\frac{1}{2}$ is physically equivalent to $\mathcal{d}_2$ defined as $\mathcal{d}_2(x^+)=\mathcal{d}_2(x^-)=\frac{1}{2}$. Therefore we define the set of mixed states $\mathcal{M}$ as the set of statistical ensembles that are physically different, which is usually represented by a density matrix. Mathematically, we can also represent physical equivalence between statistical ensembles with an equivalence operator $\mathcal{d}_1 \equiv \mathcal{d}_2$ and the set of mixed states $\mathcal{M} = \mathcal{D}_{/_\equiv}$ will be the quotient space.

@@

We can briefly see why this approach makes intuitive sense. The closer two states are in the Hilbert space, the greater the chance that one will transition to the other during a projection. Continuous evolution, then, means small deterministic changes. Unitary evolution, in particular, conserves entropy, which is also the hallmark of deterministic and reversible evolution. On the other hand, a projection can increase entropy, which is the hallmark of a transition that went out of equilibrium and is not reversible. Since any two unitary vectors can be connected by a unitary operation (i.e.~a rotation), it makes sense that all states are equilibria since they can all be connected by a deterministic and reversible process and that they all carry the same entropy. We also note that in quantum field theory, to calculate cross-sections and particle decays, one puts the initial states at minus infinity and the final states at plus infinity for processes that, in reality, take a tiny fraction of a second. This is reminiscent of a quasistatic approximation.

Finally, we note that the approach presented here does not solve the so called ``measurement problem''\cite{Genovese,Bassi}, at least not in the way it is typically framed. We still do not have a description of what happens during an arbitrary process (e.g. a projection), yet we have an explanation of why we cannot provide one in terms of a quasistatic evolution (i.e. unitary evolution) since a special case cannot describe the general one.\footnote{We purposely leave unspecified whether the faster scale processes are driven by internal or external dynamics, or by a mixture of the two. As such, this approach does not technically pick an interpretation: it merely states that whatever happens during a measurement in a given interpretation is also happening at every instant in time.}

%since the fast out-of-equilibrium process cannot be described with a quasi-static evolution.

@@

With this is mind, let us explore the following question: could we, in principle, extend the state to exhaust the description of the system? As we saw, that would mean finding a set of circumstances in which the evolution of the entirety of the system is fully determined by the system itself. That is, no part of the system is influenced by the environment in any way. Under those conditions, no interactions with the system are possible. Photons cannot interact with it, nor gravitational waves; no way to synchronize clocks between the system and the environment, no way to tell where the system is with respect to the environment. To us in the environment, within those circumstances, the system has vanished. How, then, are we supposed to study it? How are we supposed to experimentally define the properties in those conditions? How are we supposed to validate the law of evolution?

This tells us that there is a tension. On one side we can only say that something is a property of the system if it is defined independently of the environment. On the other side, we cannot completely turn off system-environment interaction or there would be no way to operationally define the property. This means that we can never have a complete independent description of the system.\footnote{Ultimately, this is why classical mechanics conceptually fails. See \cite{Carc1} for more discussion.} We need to leave out some ``unstated part'' whose future will depend on the environment. In other words, \textbf{the system always has a boundary with the environment and, through it, is in constant interaction}.

This unavoidable interaction with the environment comes into play in the definition of a system and its state. For example, we can talk about the position of a ball because we sit on the surface of the earth at around 273 K. If we were on the surface of the sun at around 5778 K, after a short time, we would not be able to talk about a ball. A state and its properties only exist because the system is in some kind of equilibrium with the environment. Therefore even if the unstated part is not part of the state, its interaction with the environment has to be ``suitable'' for the state to be defined in the first place. In other words, \textbf{a physical property of a system is well defined and measurable if and only if the constant interaction with the environment keeps it that way.}\footnote{A possible misconception is thinking that a process that does not change our state is ``doing nothing''.}

@@

Every process that has equilibria is characterized by a time scale needed to reach equilibrium. That time will set the maximum time resolution we can use with that choice of states and processes. To go to faster time scales we inevitably need to change both states and processes. For example, as we change the volume of a gas, the region against the moving wall will be compressed sooner than the opposite region, but if we wait a short while we will again obtain a uniform pressure. If we want to study that transition, we may conceptually divide the system into small volumes and we replace the pressure by a pressure field. Still, we need to assume each small volume has enough molecules to be in equilibrium. We can go into more detail, and describe the distribution of position and velocity of the molecules. Yet, we need to assume that the molecules themselves are not undergoing chemical changes. We could study the atoms of the molecules, yet we would have to assume that the atoms are stable under nuclear fission. We could study the electrons and nucleons of the atoms, yet we would have to assume they are stable under weak nuclear forces. As we move to a finer and finer description, we have faster and faster scale processes that we assume do not change the basic constituents. At each level of the description what is assumed to be in equilibrium changes and what the laws describe changes as well. Yet, the overall structure remains the same: we have a timescale $dt$ such that within each interval $[t-dt, t]$ there is a process $\mathcal{p}_t$ such that the state $\mathcal{s}_t$ is an equilibrium of $\mathcal{p}_t$. The evolution $\mathcal{E}$, then, is quasistatic in terms of the processes in $\mathcal{P}$. That is, \textbf{all deterministic laws are quasistatic evolutions in terms of system-environment interaction processes}.

We have reached, then, the second major point of this article: \textbf{the mathematical structure we used to rearrange quantum mechanics is a general structure that applies to all systems} and as such we call it the \emph{fundamental model of physics}. It is fundamental because it always applies and what changes case by case are the specifics. In all cases we are going to have a set of states that are equilibria of faster scale processes. Each faster scale process will be, in general, non-deterministic in terms of the state and will act on the space of probability distributions. The law of evolution will be a quasistatic process in terms of the faster scale processes.

In classical mechanics, the state of a ball will be given by the position and momentum of the center of mass, which will be defined over a short time scale by integrating the jiggling created by the random collisions of air particles and internal motion of the ball's molecules. That averaging process will be the same regardless of the values of position and momentum; all states are equilibria of the same process and therefore $\mathcal{P}$ contains only one element: the identity map. Therefore, while the overall structure still exists, it is mathematically trivial and can be effectively disregarded as we concentrate on the law of evolution exclusively.

@@

In this framework, then, the processes in $\mathcal{P}$ do not represent measurements, they simply represent transitions to a new equilibrium. In thermodynamics they may represent the crystallization of a supersaturated solution or the ignition of a mixture of oxygen and hydrogen to form water. In quantum mechanics they may represent the absorption of an incoming photon by a hydrogen atom or the decay of a muon into an electron and two neutrinos. In all these cases we start from a state of (possibly metastable) equilibrium and we end with a new equilibrium which is not, in general, described in terms of the initial state space. For example, water vapor is not a mixture of hydrogen and oxygen gases and a muon is not a collection of three particles. That is, in general the system passes through configurations that are not suitably described by the initial or final state space. We do not believe the similar conceptual structure to be simply a formal analogy but to represent analogue physical mechanisms. Quantum projections happen for the same reasons supersaturated solutions crystallize: a change in external or internal physical conditions that leads to a new equilibrium.

Why, then, are measurements in quantum mechanics typically associated with projections? Let us think of what a particle detector has to do: it has to take the very small signal of a particle coming through and amplify it to a macroscopic level. In the case the particle itself is absorbed, or destroyed in any way, then we are already in the realm of fast processes. In the other cases, the particle has to initiate a chain reaction that has to transfer energy stored in the detector system to the readout. The detector, then, has to be prepared in a state sufficiently stable to not change if no particle interacts with it but unstable enough that a small perturbation makes it transition to a lower energy. That is, the detector has to be prepared in a metastable state and the particle interaction has to make it transition to a more stable state. But a transition from a metastable state to a more stable state is exactly what our projections are supposed to represent.\footnote{The role of metastability in detectors has already been discussed, for example, by \cite{Daneri} and \cite{Merlin}.}

On the other hand, not all measurements are projections. In a weak measurement\cite{Tamir}, for example, the system interacts with the probe according to unitary evolution (i.e. adiabatically) and the probe itself goes through the projection. So the association of a measurement with a projection will not always work, while a process with equilibria can always be mathematically formalized as a projection.

@@

Violations of the Schroedinger equation should be expected only for processes that cannot be considered quasistatic. If we were to implement a measurement process, then, in a way that the transfer of information between the system and the probe happens in a slow and controlled fashion, this could not provide a violation of the Schroedinger equation, nor would it tell us that all projections are quasistatic processes. On the other hand, a better description of the faster scale processes given by the projections cannot be given in terms of unitary evolution, as this represents the quasistatic case. It would inevitably require a new state space as the standard quantum states can only describe equilibria of those processes. Moreover, a description at Planck time scale will ultimately fail to be continuous and quasistatic since a finite change in a finite time will not be divisible into infinitesimal adiabatic changes over infinitely many time steps.

To understand the suitable mathematical framework for those regimes where unitary evolution may not hold, we are proceeding by first identifying the physical requirements for all mathematical structures already used in physics, starting from the most basic ones like topological spaces (upon which is based all of differential geometry) and $\sigma$-algebras (upon which is based all of measure theory and probability theory). This long term effort is centered mainly around the development of an open access book\cite{Carc3} in which these issues can be explored in full detail and with a rigor more typical of mathematical disciplines. This rigor forces us to spell out the often hidden assumptions we have while constructing physical theories. By making explicit, for example, under which physically motivated circumstances time can be modeled by real numbers, or when states can be represented within Hilbert spaces, we believe we will be in a better position to understand what happens when those assumptions fail.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing--original draft preparation, X.X.; writing--review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{Funding for this work was provided in part by the MCubed program of the University of Michigan.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{This article is part of a larger project, Assumptions
	of Physics, that aims to identify a handful of physical principles from which the basic laws can be rigorously derived.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
\reftitle{References}
\begin{thebibliography}{999}

\bibitem[Carcassi(2018)]{Carc1}
G. Carcassi, C. A. Aidala, D. J. Baker, L. Bieri; From physical assumptions to classical and quantum {Hamiltonian} and {Lagrangian} particle mechanics. {\em J. Phys. Comm.} {\bf 2018}, {\em 2(4)}, 045026.
